Order Preserving Encryption Schemes: \\ Preventing the Leakage of Distribution\\ 6.857 Final Paper \\ Hrishikesh Joshi, Max Kolysh, Mari Miyachi, John Wang

### 2013-05-09 paper.tex
Working on paper.

\section{Equivalence of DCS and RTOPE}

@@

  \subsection{Equivalence}

@@

For DCS, one can see that moving left or right from the root element depends on the relative size of the root element with the new element being inserted or queried.

>>>>

\section{Relationship Between DCS and RTOPE}

@@

  \subsection{Expectational Equivalence}

@@

For DCS, one can see that moving left or right from the root element depends on the relative size of the root element with the new element being inserted or queried. For example, if $x$ is the value of a repeated plaintext, then DCS will mutate $p$ into $p + r$ where $r \in [0,1)$ are some random bits. Moving left at the root means that $p_1 < p_r$ where $p_r$ is the root value. This means that $p + r_1 < p + r_r$, which is equivalent to saying $r_1 < r_r$. Thus, moving left at the root is just the probability that the random number $r_1$ is smaller than the random number $r_r$ picked at the root.

  Now let us examine some series of moves down the tree when attempting to query or insert some node with plaintext value $x$, denoted by the sequence
  \begin{eqnarray}
    \{ m_0(x), m_1(x), \ldots, m_k(x) \}
  \end{eqnarray}

  We shall drop the $x$ for convenience and commonly refer to moves as $m_i$. We see that $m_i$ can take on two possibilities, 0 for left or 1 for moving right, and we can characterize the moves:
  \begin{eqnarray}
    m_i(x) = \left\{ \begin{array}{l l}
        0 & \textrm{if } p_i > x \\
        1 & \textrm{else}
  \end{eqnarray}

  Here $p_i$ is the underlying plaintext value of the node at the $i$th move.

  We shall proceed to show that the two schemes actually produce the same expected tree. In order to do this, we first prove a lemma.
  \begin{lemma}
    Let $\{X_i\}_{i=1}^n$ be a sequence of $n$ independent uniform random variables chosen from the interval $[0,1)$. Let $X_{n+1}$ be another uniform random varaible on the interval $[0,1)$. The probability that $x_{n+1}$ is the $j$th smallest item is $1/(n+1)$.
  \end{lemma}
  \begin{proof}
    For the proof, we rely on the fact that the $n$ random variables are independent. We note that the $n+1$st random variable can be thought of as the next random variable in the sequence. Moreover, since all of the random variables are independently drawn from the same uniform distribution, we see that we are really drawing a set of $n+1$ uniform random variables which can be chosen at the same time.

    It is clear that the probability of any $x_i$ being the $j$th smallest item is the same, because all of the random variables are drawn independently. This means that $Pr[X_{n+1} = S_j]$ were $S_j$ is the $j$th smallest item can be given by the expression:
    \begin{eqnarray}
      Pr[X_{n+1} = S_j] = Pr[X_{n} = S_j] = \ldots = Pr[X_{1} = S_j]
    \end{eqnarray}

    For all values of $j \in \{1, \ldots, n+1\}$. Since exactly one $x_i$ is the $j$th smallest element, we see that $\sum_{i=1}^{n+1} Pr[X_i = X_j] = 1$. This implies that $Pr[X_i = S_j] = 1/(n+1)$ which further implies that $Pr[X_{n+1} = S_j] = 1/(n+1)$ for all $j$. This completes the proof.
  \end{proof}

  This lemma allows us to show that DCS and RTOPE have identical move distributions, which will show that the two schemes have the same expected tree structure.

  \begin{table}
    \begin{tabular}{l | c | c | c | c | c | c}
      Trials & 10 & 20 & 50 & 100 & 200 & 500 \\
      \hline \hline
      1000 & 0.111 & 0.122 & 0.179 & 0.249 & 0.363 & 0.537 \\
      5000 & 0.093 & 0.062 & 0.075 & 0.104 & 0.162 & 0.241 \\
     10000 & 0.089 & 0.059 & 0.055 & 0.071 & 0.106 & 0.176 \\
     50000 & 0.090 & 0.047 & 0.028 & 0.037 & 0.052 & 0.077 \\
    100000 & 0.090 & 0.047 & 0.021 & 0.026 & 0.033 & 0.059 \\
    200000 & 0.091 & 0.047 & 0.021 & 0.018 & 0.022 & 0.040 \\
    500000 & 0.091 & 0.047 & 0.019 & 0.013 & 0.017 & 0.025 \\
   1000000 & 0.090 & 0.047 & 0.019 & 0.011 & 0.011 & 0.017 \\
    \end{tabular}
    \caption{Tests}
  \end{table}
